MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
more updates to bib
moved sections around

\section{Threat Model}
TODO
\section{Related Work}
%not sure this section is really necessary because of the last section
Phan and Mingard show that a malicious device can impersonate a legitimate device and communicate with another legitimate device by making the user enter whichever authentication pin it chooses \cite{phan2012analyzing}.

@@

The most relevant research to our own Basic BT attack on keyboard \cite{cuthbertbluetooth}

\section{The Attack}
There are 4 main steps to executing the attack:
\begin{enumerate}
\item Find Bluetooth Address of the keyboard
\item Execute DoS attack against victim
\item Pair with keyboard and victim
\item Forward keystrokes to victim
\end{enumerate}
TODO 
\subsection{Finding the Keyboard Bluetooth Address}
The work relies on the assumption that we can find the MAC address of the keyboard easily and quickly using a Bluetooth sniffer and packet capturing software such as Kismet[link]. Although it is possible to manually program a Bluetooth card, it is possible to obtain hardware that sniffs and integrates with Kismet. Project Ubertooth provides both hardware and a plugin for Kismet that allows you to promiscuously sniff Bluetooth packets and displays the MAC address from whatever device is sending out the packets.

@@

Worked for Windows Vista and Linux Ubuntu with BlueZ but did not work for Windows 7 \cite{cuthbertbluetooth}

@@

\subsection{Attack}
Note about pairing before hand
\begin{verbatim}
sudo hidd --connect <keyboard-address>
\end{verbatim}

@@

\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

>>>>

\section{Related Work}
%not sure this section is really necessary because of the last section
Phan and Mingard show that a malicious device can impersonate a legitimate device and communicate with another legitimate device by making the user enter whichever authentication pin it chooses \cite{phan2012analyzing}.

@@

The most relevant research to our own Basic BT attack on keyboard \cite{cuthbertbluetooth}
\section{Threat Model}
TODO

\section{Attack Overview}
There are 4 main steps to executing the attack:
\begin{enumerate}
\item Find Bluetooth Address of the keyboard
\item Execute DoS attack against victim
\item Pair with keyboard and victim
\item Forward keystrokes to victim
\end{enumerate}
TODO 
\subsection{Finding the Keyboard Bluetooth Address}
The work relies on the assumption that we can find the MAC address of the keyboard easily and quickly using a Bluetooth sniffer and packet capturing software such as Kismet[link]. Although it is possible to manually program a Bluetooth card, it is possible to obtain hardware that sniffs and integrates with Kismet. Project Ubertooth provides both hardware and a plugin for Kismet that allows you to promiscuously sniff Bluetooth packets and displays the MAC address from whatever device is sending out the packets.

@@

Worked for Windows Vista and Linux Ubuntu with BlueZ but did not work for Windows 7 \cite{cuthbertbluetooth}
Dos attack\cite{bandyopadhyay2010information}

@@

\subsection{Implementation}
Note about pairing before hand
\begin{verbatim}
sudo hidd --connect <keyboard-address>
\end{verbatim}

@@
